Joint maximum-likelihood of phylogenies and ancestral states is not consistent

### 2018-06-15 appendix.tex
argument updates

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
    \hline
$\siteSplit_j$  & $p_{\siteSplit_j}$ &$\Pr(\siteSplitRV=\siteSplit_j \mid \tau_1,\{x,y,x,y,w\})$\\
    \hline
    $\emptyset$ & $p_{\emptyset}$   &$1+x^2+y^2+4xyw+x^2y^2$\\
    $\{1\}$     & $p_{1}$   &$1-x^2+y^2-x^2y^2$\\
    $\{2\}$     & $p_{2}$   &$1+x^2-y^2-x^2y^2$\\
    $\{3\}$     & $p_{3}$   &$1-x^2+y^2-x^2y^2$\\
    $\{1,2\}$   & $p_{12}$   &$1-x^2-y^2+x^2y^2$\\
    $\{1,3\}$   & $p_{13}$   &$1+x^2+y^2-4xyw+x^2y^2$\\
    $\{2,3\}$   & $p_{23}$   &$1-x^2-y^2+x^2y^2$\\
    $\{1,2,3\}$ & $p_{123}$   &$1+x^2-y^2-x^2y^2$\\
    \hline
\end{tabular}
\caption{Site split probabilities $p_{\siteSplit_j}$ on the InvFels tree $\tau_1$ with $t=\{x,y,x,y,w\}$ obtained using the Hadamard transform.
All values multiplied by $1/8$.}
\label{tab:sitepatprob}
\end{table}

@@

It remains to show the converse: if $x_1=x_2$ and $y_1=y_2$ then we obtain a unique estimate of $\tilde{t}$ when performing joint inference maximizing \eqref{eq:profile_likelihood}.
To do so, we show the Hessian of the joint likelihood term is negative definite.
First, we decompose the likelihood into the divergence and partial log-likelihood terms as in \eqref{eq:log_likelihood_simplified}.
Assume $x_1=x_2=x$ and $y_1=y_2=y$ so that $t=\{x,y,x,y,w\}$.
We restrict our attention to $x,y\in(0,1)$, i.e., cases where $0<p_{\siteSplit_j}<1$ for all $\siteSplit_j$.
Additionally, we exclude the infinite branch length case of $w=0$.
Recall the divergence
\[
\shannonDivergence_{\tau_1,t^*}(\tau_1,t) = \sum_{j=1}^\nSiteSplits \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t^*)\cdot\log \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t).
\]
where data is generated on the InvFels tree with two top branches of fidelity $x^*$ and all other branches of fidelity $y^*$ (Fig.~\ref{fig:farris-fels-top}).
By Gibbs inequality, this function attains a unique maximum when
\[
\Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t) = \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t^*)
\]
for all $j=1,\ldots,\nSiteSplits$ with $t^*=\{x^*,y^*,x^*,y^*,y^*\}$.
Referring to Table~\ref{tab:sitepatprob}, we set up simultaneous equations as follows.
The sum of generating probabilities for site splits $\{3\}$ and $\{1,2\}$ yields
\[
2-2(x^*)^2 = 2-2x^2
\]
and for $\{2\}$ and $\{1,2\}$ yields
\[
2-2(y^*)^2 = 2-2y^2.
\]
implying $x=x^*$ and $y=y^*$.
Setting these parameters to their optima, the difference of generating probabilities for site splits $\emptyset$ and $\{1,3\}$ yields
\[
8x^*(y^*)^2 = 8x^*y^*w
\]
implying $w=x^*$.
The unique maximum is $\hat{t}=\{x^*,y^*,x^*,y^*,y^*\}$, and thus the Hessian of $\shannonDivergence$ is negative definite.

@@

We now consider the case where there may be more than one functional form that maximizes the partial likelihood over ancestral state splits for a site split.
Table~\ref{tab:likelihoods} shows that an ambiguity in the form of the partial likelihood occurs in one of four cases:
\[
1: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1-w)(1+y)^2 > (1+x)^2(1+w)(1-y)^2,
\]
\[
2: (1+x)^2(1-w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2 > (1-x)^2(1+w)(1+y)^2,
\]
\[
3: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2 > (1+x)^2(1-w)(1+y)^2,
\]
or
\[
4: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1-w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2.
\]
In case 1, the equality implies $w=2x/(1+x^2)$.
Plugging this into Table~\ref{tab:likelihoods}, we see the partial log-likelihood, again suppressing constants with respect to $x$ and the initial $1/32$ constant, is
\begin{align*}
\tilde{\ell}(x) &\propto (2-p_1-p_3-p_{12}-p_{23}-2p_{13})\log(1+x) \\
&\qquad + (p_1+p_3+p_{12}+p_{23}+2p_{13})\log(1-x) \\
&\qquad + 2\log(1+x)-\log(1+x^2).
\end{align*}
Call
\[
c := p_1+p_3+p_{12}+p_{23}+2p_{13}
\]
so that straightforward calculus reveals
\begin{align*}
\tilde{\ell}''(x) &= \frac{4x^2}{(1+x^2)^2}-\frac{4-c}{(1+x)^2}-\frac{c}{(1-x)^2}\\
                  &= \left(\frac{4x^2}{(1+x^2)^2}-\frac{4}{(1+x)^2}\right)+c\left(\frac{1}{(1+x)^2}-\frac{1}{(1-x)^2}\right).
\end{align*}
The term on the right is negative as $c \ge 0$ and $0 < x < 1$.
The term on the left can be written as
\[
\frac{4}{(\frac{1}{x}+x)^2}-\frac{4}{(1+x)^2},
\]
which for $0<x<1$ is negative so that $\tilde{\ell}''(x) \le 0$.
Case 2 follows the same argument but for $y$.
In case 3, the ambiguity implies $x=y$, which yields a partial log-likelihood of the form \eqref{eq:partial-x-form} multiplied by two, and thus has negative second derivative.
Finally, case 4 implies $x=y$ and $w=2x/(1+x^2)$, and a combination of the above arguments shows we again have a negative second derivative.
Thus, for $\tilde{t}=\{x_1,y_1,x_2,y_2,w\}$, there is a unique maximum of $\ell_{\tau_1,t^*}(\tau_1, \tilde{t})$ if and only if $x_1=x_2$ and $y_1=y_2$, yielding our identifiability criteria.

Given the above, with the symmetry of the likelihood we let $x_1=x_2=x$ and $y_1=y_2=y$.
The Felsenstein tree does not admit this property, but, since we are interested in a lower bound for this tree, we simplify the objective function by constraining $x_1=x_2$ and $y_1=y_2$ similarly.

@@

We next construct a lower bound on the Felsenstein tree partial likelihood.
In general, taking
\[
\hat{t} = \argmax_{t} \ \tilde{\ell}_{\tau^*,t^*}(\tau, t).
\]
we see
\[
\max_{t} \ \ell_{\tau^*,t^*}(\tau, t) \ge
    \shannonDivergence_{\tau^*,t^*}(\tau,\hat{t})
    + \tilde{\ell}_{\tau^*,t^*}(\tau, \hat{t})
\]
is a lower bound for the joint maximum of \eqref{eq:log_likelihood_simplified}.
In the Felsenstein case, there are many more optimal internal states depending on branch lengths than in the InvFels case (see the lower table of Table~\ref{tab:likelihoods}).
We first bound the entire likelihood below and then proceed with joint inference.
To obtain a lower bound for the likelihood we replace $1+w$ with $1-w$ in Table~\ref{tab:likelihoods} for $\tau = \tau_2$; in this case, we resolve many of the ambiguous likelihood terms.
For example, for site split $\{1,2\}$, after we replace the $1+w$ term for $\ancestralSplitPartition_j(\tau, t)=\{\emptyset, \{1,2\}\}$ with $1-w$, we have
\[
\max\left((1+x)^2 (1-w)(1+y)^2, (1+x)(1-x)(1-w)(1+y)(1-y)\right)
\]
where since
\[
(1+x)^2 (1-w)(1+y)^2 > (1+x)(1-x)(1-w)(1+y)(1-y),
\]
the maximum for this site split can be bounded below by $(1+x)^2 (1-w)(1+y)^2$.
For the other site splits we consider two cases.
If $(1+x)(1-y) > (1-x)(1+y)$, then
\[
(1+x)^2(1-w)(1+y)(1-y) > (1+x)(1-x)(1-w)(1+y)^2
\]
meaning the cases $\{1\}, \{2\}, \{3\}$ and $\{1,2,3\}$ will have likelihoods bounded below by
\[
(1+x)^2(1-w)(1+y)(1-y).
\]
For the cases $\{1,3\}$ and $\{2,3\}$ and the same condition, we have
\[
(1+x)^2(1-w)(1-y)^2 > (1-x)^2(1-w)(1+y)^2
\]
and
\[
(1+x)^2(1-w)(1-y)^2 > (1+x)(1-x)(1-w)(1+y)(1-y),
\]
yielding lower bounds of
\[
(1+x)^2(1-w)(1-y)^2
\]
in these cases.
The partial likelihood in this case is then bounded below by
\begin{align*}
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    &\ge      p_{\emptyset}  \cdot\log((1+x)^2   (1-w)(1+y)^2) \\
    &\qquad + p_{1}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{2}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{3}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{12}         \cdot\log((1+x)^2   (1-w)(1+y)^2) \\
    &\qquad + p_{123}        \cdot\log((1+x)^2   (1-w)(1+y)(1-y))\\
    &\qquad + p_{13}         \cdot\log((1+x)^2   (1-w)(1-y)^2) \\
    &\qquad + p_{23}         \cdot\log((1+x)^2   (1-w)(1-y)^2).
\end{align*}
When $(1+x)(1-y) < (1-x)(1+y)$, similar arguments yield the lower bound
\begin{align*}
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    &\ge      p_{\emptyset}  \cdot\log((1+x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{1}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    &\qquad + p_{2}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    &\qquad + p_{3}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    %See above.
    &\qquad + p_{12}         \cdot\log((1+x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{123}        \cdot\log((1+x)(1-x)(1-w)(1+y)^2)\\
    &\qquad + p_{13}         \cdot\log((1-x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{23}         \cdot\log((1-x)^2    (1-w)(1+y)^2).
\end{align*}
Letting
\[
b = p_{1}+p_{2}+p_{3}+p_{123}
\]
yields
\[
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    \ge      2\cdot\log(1+x)
    + (2-b)  \cdot\log(1+y)
    + b      \cdot\log(1-y)
    + \log(1-w)
\]
for the first lower bound, and we get the equivalent expression for the second lower bound by exchanging $x$ and $y$.
Maximizing either lower bound over $t$, we obtain
\[
\tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
\ge      2\cdot\log(2)
+ (2-b)  \cdot\log(2-b)
+ b      \cdot\log(b),
\]
i.e., the maximum is achieved at $\{1,1-b,0\}$.
Our lower bound is
\[
C_1(x^*, y^*) := \shannonDivergence_{\tau_1,t^*}(\tau_2,\{1,1-b,0\}) + 2\cdot\log(2) + (2-b)\cdot\log(2-b) + b\cdot\log(b).
\]
See Fig.~\ref{fig:inconsistency-farris} for the values of $0 < p_{x^*}, p_{y^*} < 1$ with $p_{x^*}=(1-x^*)/2$ and $p_{y^*}=(1-y^*)/2$ where $C_1(x^*, y^*) > C_0(x^*, y^*)$ and joint inference is inconsistent.
\end{proof}

>>>>

\begin{table}[ht]
\centering
\begin{tabular}{|l|l|l|}
    \hline
$\siteSplit_j$  & $p_{\siteSplit_j}$ &$\Pr(\siteSplitRV=\siteSplit_j \mid \tau_1,\{x,y,x,y,w\})$\\
    \hline
    $\emptyset$ & $p_{\emptyset}$   &$1+x^2+y^2+4xyw+x^2y^2$\\
    $\{1\}$     & $p_{1}$           &$1-x^2+y^2-x^2y^2$\\
    $\{2\}$     & $p_{2}$           &$1+x^2-y^2-x^2y^2$\\
    $\{3\}$     & $p_{3}$           &$1-x^2+y^2-x^2y^2$\\
    $\{1,2,3\}$ & $p_{123}$         &$1+x^2-y^2-x^2y^2$\\
    $\{1,2\}$   & $p_{12}$          &$1-x^2-y^2+x^2y^2$\\
    $\{2,3\}$   & $p_{23}$          &$1-x^2-y^2+x^2y^2$\\
    $\{1,3\}$   & $p_{13}$          &$1+x^2+y^2-4xyw+x^2y^2$\\
    \hline
\end{tabular}
\caption{Site split probabilities $p_{\siteSplit_j}$ on the InvFels tree $\tau_1$ with $t=\{x,y,x,y,w\}$ obtained using the Hadamard transform.
All values multiplied by $1/8$.}
\label{tab:sitepatprob}
\end{table}

@@

We now show the converse: if $x_1=x_2$ and $y_1=y_2$ then we obtain a unique estimate of $\tilde{t}$ when performing joint inference maximizing \eqref{eq:profile_likelihood}.
To do so, we show the Hessian of the joint likelihood term is negative definite.
First, we decompose the likelihood into the divergence and partial log-likelihood terms as in \eqref{eq:log_likelihood_simplified}.
Assume $x_1=x_2=x$ and $y_1=y_2=y$ so that $t=\{x,y,x,y,w\}$.
We restrict our attention to $x,y\in(0,1)$, i.e., cases where $0<p_{\siteSplit_j}<1$ for all $\siteSplit_j$.
Additionally, we exclude the infinite branch length case of $w=0$.
Recall the divergence
\[
\shannonDivergence_{\tau_1,t^*}(\tau_1,t) = \sum_{j=1}^\nSiteSplits \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t^*)\cdot\log \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t).
\]
where data is generated on the InvFels tree with two top branches of fidelity $x^*$ and all other branches of fidelity $y^*$ (Fig.~\ref{fig:farris-fels-top}).
By Gibbs inequality, this function attains a unique maximum when
\[
\Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t) = \Pr(\siteSplitRV=\siteSplit_j \mid \tau_1, t^*)
\]
for all $j=1,\ldots,\nSiteSplits$ with $t^*=\{x^*,y^*,x^*,y^*,y^*\}$.
Referring to Table~\ref{tab:sitepatprob}, we set up simultaneous equations as follows.
The sum of generating probabilities for site splits $\{3\}$ and $\{1,2\}$ yields
\[
2-2(x^*)^2 = 2-2x^2
\]
and for $\{2\}$ and $\{1,2\}$ yields
\[
2-2(y^*)^2 = 2-2y^2.
\]
implying $x=x^*$ and $y=y^*$.
Setting these parameters to their optima, the difference of generating probabilities for site splits $\emptyset$ and $\{1,3\}$ yields
\[
8x^*(y^*)^2 = 8x^*y^*w
\]
implying $w=y^*$.
The unique maximum is $\hat{t}=\{x^*,y^*,x^*,y^*,y^*\}$, and thus the Hessian of $\shannonDivergence$ is negative definite.

@@

We have shown above that, for each ancestral state split, we obtain a unique maximum performing joint maximization of the likelihood.
It may be the case that separate ancestral state splits yield different estimates with the same likelihood value.
As joint inference obtains estimates by maximizing over latent variables, if a single functional form is maximal then there is a single solution that is feasible for the joint optimization procedure to recover.
We now consider the case where there may be more than one functional form that maximizes the partial likelihood over ancestral state splits for a site split.
To show joint optimzation results in a unique maximum, it suffices to consider the cases where an ambiguity in the form of the partial likelihood occurs.
Table~\ref{tab:likelihoods} shows this occurs in one of four cases:
\[
1: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1-w)(1+y)^2 > (1+x)^2(1+w)(1-y)^2,
\]
\[
2: (1+x)^2(1-w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2 > (1-x)^2(1+w)(1+y)^2,
\]
\[
3: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2 > (1+x)^2(1-w)(1+y)^2,
\]
or
\[
4: (1-x)^2(1+w)(1+y)^2 = (1+x)^2(1-w)(1+y)^2 = (1+x)^2(1+w)(1-y)^2.
\]
In case 1, the equality implies $w=2x/(1+x^2)$, and in case 2 $w=2y/(1+y^2)$.
Case 3 implies $x=y$, and, finally, case 4 is a combination of these.
These cases may or may not indicate an identifiability issue with the joint inference procedure, as showing a unique estimate arises in each case is nontrivial.
While we may lose identifiability, the set of parameters for which these equalities hold and, additionally, do not yield a unique maximum will encompass a minority of the parameter space.

Thus, for $\tilde{t}=\{x_1,y_1,x_2,y_2,w\}$, there is a unique maximum of $\ell_{\tau_1,t^*}(\tau_1, \tilde{t})$ if and only if $x_1=x_2$ and $y_1=y_2$ for the majority of the parameter space, yielding our identifiability criteria.
With the symmetry of the likelihood we let $x_1=x_2=x$ and $y_1=y_2=y$.
The Felsenstein tree does not admit this property, but, since we are interested in a lower bound for this tree, we simplify the objective function by constraining $x_1=x_2$ and $y_1=y_2$ similarly.

@@

We next construct a lower bound on the Felsenstein tree partial likelihood.
In general, taking
\hat{t} = \argmax_{t} \ \tilde{\ell}_{\tau^*,t^*}(\tau, t).
we see
\max_{t} \ \ell_{\tau^*,t^*}(\tau, t) \ge
    \shannonDivergence_{\tau^*,t^*}(\tau,\hat{t})
    + \tilde{\ell}_{\tau^*,t^*}(\tau, \hat{t})
is a lower bound for the joint maximum of \eqref{eq:log_likelihood_simplified}.
In the Felsenstein case, there are many more optimal internal states depending on branch lengths than in the InvFels case (see the lower table of Table~\ref{tab:likelihoods}).
We first bound the entire likelihood below and then proceed with joint inference.
To obtain a lower bound for the likelihood we replace $1+w$ with $1-w$ in Table~\ref{tab:likelihoods} for $\tau = \tau_2$; in this case, we resolve many of the ambiguous likelihood terms.
For example, for site split $\{1,2\}$, after we replace the $1+w$ term for $\ancestralSplitPartition_j(\tau, t)=\{\emptyset, \{1,2\}\}$ with $1-w$, we have
\max\left((1+x)^2 (1-w)(1+y)^2, (1+x)(1-x)(1-w)(1+y)(1-y)\right)
where since
(1+x)^2 (1-w)(1+y)^2 > (1+x)(1-x)(1-w)(1+y)(1-y),
the maximum for this site split can be bounded below by $(1+x)^2 (1-w)(1+y)^2$.
For the other site splits we consider three cases.
If $(1+x)(1-y) > (1-x)(1+y)$, then
(1+x)^2(1-w)(1+y)(1-y) > (1+x)(1-x)(1-w)(1+y)^2
meaning the cases $\{1\}, \{2\}, \{3\}$ and $\{1,2,3\}$ will have likelihoods bounded below by
(1+x)^2(1-w)(1+y)(1-y).
For the cases $\{1,3\}$ and $\{2,3\}$ and the same condition, we have
(1+x)^2(1-w)(1-y)^2 > (1-x)^2(1-w)(1+y)^2
(1+x)^2(1-w)(1-y)^2 > (1+x)(1-x)(1-w)(1+y)(1-y),
yielding lower bounds of
(1+x)^2(1-w)(1-y)^2
in these cases.
The partial likelihood in this case is then bounded below by
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    &\ge      p_{\emptyset}  \cdot\log((1+x)^2   (1-w)(1+y)^2) \\
    &\qquad + p_{1}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{2}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{3}          \cdot\log((1+x)^2   (1-w)(1+y)(1-y)) \\
    &\qquad + p_{12}         \cdot\log((1+x)^2   (1-w)(1+y)^2) \\
    &\qquad + p_{123}        \cdot\log((1+x)^2   (1-w)(1+y)(1-y))\\
    &\qquad + p_{13}         \cdot\log((1+x)^2   (1-w)(1-y)^2) \\
    &\qquad + p_{23}         \cdot\log((1+x)^2   (1-w)(1-y)^2).
When $(1+x)(1-y) < (1-x)(1+y)$, similar arguments yield the lower bound
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    &\ge      p_{\emptyset}  \cdot\log((1+x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{1}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    &\qquad + p_{2}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    &\qquad + p_{3}          \cdot\log((1+x)(1-x)(1-w)(1+y)^2) \\
    %See above.
    &\qquad + p_{12}         \cdot\log((1+x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{123}        \cdot\log((1+x)(1-x)(1-w)(1+y)^2)\\
    &\qquad + p_{13}         \cdot\log((1-x)^2    (1-w)(1+y)^2) \\
    &\qquad + p_{23}         \cdot\log((1-x)^2    (1-w)(1+y)^2).
Finally, if $(1+x)(1-y) = (1-x)(1+y)$, $x=y$ and the lower bound will be less than the other cases.
Letting
b = p_{1}+p_{2}+p_{3}+p_{123}
yields
    \tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
    \ge      2\cdot\log(1+x)
    + (2-b)  \cdot\log(1+y)
    + b      \cdot\log(1-y)
    + \log(1-w)
for the first lower bound, and we get the equivalent expression for the second lower bound by exchanging $x$ and $y$.
Moreover, the divergence quanitity is unchanged when exchanging $x$ and $y$ provided $w=0$.
Maximizing either lower bound over $t$, we obtain
\tilde{\ell}_{\tau_1,t^*}(\tau_2, t)
\ge      2\cdot\log(2)
+ (2-b)  \cdot\log(2-b)
+ b      \cdot\log(b),
i.e., the maximum is achieved at $\{1,1-b,0\}$.
Our lower bound is
C_1(x^*, y^*) := \shannonDivergence_{\tau_1,t^*}(\tau_2,\{1,1-b,0\}) + 2\cdot\log(2) + (2-b)\cdot\log(2-b) + b\cdot\log(b).
See Fig.~\ref{fig:inconsistency-farris} for the values of $0 < p_{x^*}, p_{y^*} < 1$ with $p_{x^*}=(1-x^*)/2$ and $p_{y^*}=(1-y^*)/2$ where $C_1(x^*, y^*) > C_0(x^*, y^*)$ and joint inference is inconsistent.
